Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/introduction.tex
Fixed Agda version.
Cosmetic changes.
[ paper ] lots of changes.

This paper has been organized in the following way.
In Section~\ref{sec:limitations-type-theory} some limitations of type theory
are discussed from proof-reconstruction point view.
In Section~\ref{sec:metis-language-and-proofs}, we introduce the
\Metis prover.
In Section~\ref{sec:proof-reconstruction} we show our
approach to reconstruct \Metis proofs.
Related work is described in Section~\ref{sec:related-work}.
Conclusions and suggestions for future work are  presented in
Section~\ref{sec:conclusions}.

@@

The proof-reconstruction was carried on for \Metis~v2.3
release~2017102, and the accompanying source code was tested with
\Agda~v2.3, \Agda standard library~v0.14 and \prg{GHC}~v.8.2.1.

>>>>

This paper has been organized in the following way.
In Section~\ref{sec:type-theory} some limitations of type theory
are discussed from proof-reconstruction point view.
In Section~\ref{sec:metis-language-and-proofs}, we introduce the
\Metis prover.
In Section~\ref{sec:proof-reconstruction} we show our
approach to reconstruct \Metis proofs.
Related work is described in Section~\ref{sec:related-work}.
Conclusions and suggestions for future work are  presented in
Section~\ref{sec:conclusions}.

@@

The proof-reconstruction was carried on for \Metis~2.3
(release~20170822), and the accompanying source code was tested with
\Agda~2.5.3, \Agda standard library~0.14 and \prg{GHC}~8.2.1.
